Supplememtary materials for:

### 2020-07-23 article.Rmd
Made some minor changes to the article and extensions, mostly format

---
title: \singlespacing A closer look at fixed effects regression in structural equation modeling using \texttt{lavaan}
author: Henrik Kenneth Andersen
abstract: "This article provides an in-depth look at fixed effects regression in the structural equation modeling (SEM) framework, specifically the application of fixed effects in the `lavaan` package for `R`. It is meant as a applied guide for researchers, covering the underlying model specification, syntax, and summary output. Online supplementary materials further discuss various common extentsions to the basic fixed-effect model, demonstrating how to relax model assumptions, deal with measurement error in both the dependent and independent variables, and include time-invariant predictors in a type of hybrid fixed-/ random effects model. \\par  \\textbf{Keywords:} Fixed effects, structural equation modeling, lavaan, R, panel analysis" 
note: "Preprint version, please do not cite without permission."
date: "`r Sys.Date()`"
output: 
  pdf_document:
    fig_caption: yes
    number_sections: yes
    includes: 
      in_header: header.tex
documentclass: article
classoption: a4paper
urlcolor: blue
link-citations: yes
bibliography: references.bib   
---

@@

There are a number of articles describing basic concept of panel model regression, and FE regression in SEM [e.g., @Allison2011; @Bollen2010; @Teachman2001]. This article is intended as a \textit{practical guide} for researchers looking for in-depth help with specifying FE models in SEM. It focuses on the `lavaan` [@R-lavaan] package for `R` [@R-base]. While `Mplus` [@Mplus] is arguably the most robust SEM software currently available (in terms of features like alignment, latent variable interactions, for example) , the `lavaan` package has many benefits. First, like `R` it is open source and completely free. For researchers dipping their toes into SEM, there is no financial barrier to try, and no risk if they decide it is not for them. Second, the implementation of `lavaan` in the larger `R` environment is an enormous advantage. Instead of poring over reams of plain text, copying out coefficients by hand, every part of the `lavaan` output is available as an object. This means that all aspects of the model, from fit indices, to coefficients and standard errors, to the model matrices, can be accessed and easily integrated into tables and plots. Furthermore, `R` can be used for a great deal of applications. It can be used to manage and manipulate as well as simulate data, perform symbolic algebra, run more traditional analyses (e.g., multiple regression, logistic regression, principal component analysis), etc. Once one is comfortable using `R`, there is no longer any need to switch between different software for data preparation and analysis.

>>>>

---
title: \singlespacing A closer look at fixed effects regression in structural equation modeling using \texttt{lavaan}
author: Henrik Kenneth Andersen
abstract: "This article provides an in-depth look at fixed effects regression in the structural equation modeling (SEM) framework, specifically the application of fixed effects in the `lavaan` package for `R`. It is meant as a applied guide for researchers, covering the underlying model specification, syntax, and summary output. Online supplementary materials further discuss various common extentsions to the basic fixed-effect model, demonstrating how to relax model assumptions, deal with measurement error in both the dependent and independent variables, and include time-invariant predictors in a type of hybrid fixed-/ random effects model. \\par  \\textbf{Keywords:} Fixed effects, structural equation modeling, lavaan, R, panel analysis" 
note: "Preprint version, please do not cite without permission."
date: "`r Sys.Date()`"
geometry: margin=1in
output: 
  pdf_document:
    fig_caption: yes
    number_sections: yes
    includes: 
      in_header: header.tex
documentclass: article
classoption: a4paper
urlcolor: blue
link-citations: yes
bibliography: references.bib   
fontsize: 12pt
---

@@

There are a number of articles describing basic concept of panel model regression, and FE regression in SEM [e.g., @Allison2011; @Bollen2010; @Teachman2001]. This article is intended as a \textit{practical guide} for researchers looking for in-depth help with specifying FE models in SEM. It focuses on the `lavaan` [@R-lavaan] package for `R` [@R-base]. While `Mplus` [@Mplus] is arguably the most robust SEM software currently available (in terms of features like alignment, latent variable interactions, for example), the `lavaan` package has many benefits. First, like `R` it is open source and completely free. For researchers dipping their toes into SEM, there is no financial barrier to try, and no risk if they decide it is not for them. Second, the implementation of `lavaan` in the larger `R` environment is an enormous advantage. Instead of poring over reams of plain text, copying out coefficients by hand, every part of the `lavaan` output is available as an object. This means that all aspects of the model, from fit indices, to coefficients and standard errors, to the model matrices, can be accessed and easily integrated into tables and plots. Furthermore, `R` can be used for a great deal of applications. It can be used to manage and manipulate as well as simulate data, perform symbolic algebra, run more traditional analyses (e.g., multiple regression, logistic regression, principal component analysis), etc. Once one is comfortable using `R`, there is no longer any need to switch between different software for data preparation and analysis.

### 2020-07-23 extensions.Rmd
Made some minor changes to the article and extensions, mostly format

---
title: "Supplememtary examples for:"
#author: "Henrik Kenneth Andersen"
#date: "`r Sys.Date()`"
output: 
  pdf_document:
    fig_caption: yes
    number_sections: yes
    includes: 
      in_header: header.tex
documentclass: article
classoption: a4paper
urlcolor: blue
link-citations: yes
bibliography: references.bib   
---

@@

Andersen, Henrik K. (2020). A closer look at fixed-effects regression in structural equation modeling using lavaan.

@@

@@

## A comparison with non-SEM methods using the simulated data

>>>>

---
title: "Supplememtary materials for:"
#author: "Henrik Kenneth Andersen"
#date: "`r Sys.Date()`"
geometry: margin=1in
output: 
  pdf_document:
    fig_caption: yes
    number_sections: yes
    includes: 
      in_header: header.tex
documentclass: article
classoption: a4paper
urlcolor: blue
link-citations: yes
bibliography: references.bib   
fontsize: 12pt
---

\vspace{-75pt}

@@

[Andersen, Henrik K. 2020. "A closer look at fixed effects regression in structural equation modeling using \texttt{lavaan}"](https://github.com/henrik-andersen/FE-SEM/blob/master/article.pdf).

@@

---

@@

# A comparison with non-SEM methods
